### 2016-05-16 text/Chapter08.tex
Spell checking

Another approach for embedding computations into the type system has been pioneered by F\#
\emph{type providers} \cite{app-inforich}. Technically, type providers are compiler extensions
that generate types based on external data sources or other information in order to provide easy
access to data or services. A similar approach could be used for embedding \emph{algberas} such
as coeffect algebras into the type system. An \emph{algebra provider} would then be a library that
specifies the objects of the algebra, its equational laws and generalization rules for type inference.
This could provide an easy-to-use way of embedding coeffect tracking in pragmatic languages
such as F\#. It is worth noting that the mechanism could also subsume F\# units of measure
\cite{types-units-of-measure}; these could be alternatively provided via one such \emph{algebra
provider}.

@@

Finally, we considered an alternative approach to practical implementation of coeffect systems.
Rather than building a specialized programming language (as we did in Chapter~\ref{ch:impl}), we
discuss the technical requirements for embedding coeffects as a domain-specific language (DSL) into
a statically-typed functional language with rich type system such as Haskell. This can be done by
following the succesfull example of Haskell's ``do'' notation.

>>>>

Another approach for embedding computations into the type system has been pioneered by F\#
\emph{type providers} \cite{app-inforich}. Technically, type providers are compiler extensions
that generate types based on external data sources or other information in order to provide easy
access to data or services. A similar approach could be used for embedding \emph{algebras} such
as coeffect algebras into the type system. An \emph{algebra provider} would then be a library that
specifies the objects of the algebra, its equational laws and generalization rules for type inference.
This could provide an easy-to-use way of embedding coeffect tracking in pragmatic languages
such as F\#. It is worth noting that the mechanism could also subsume F\# units of measure
\cite{types-units-of-measure}; these could be alternatively provided via one such \emph{algebra
provider}.

@@

Finally, we considered an alternative approach to practical implementation of coeffect systems.
Rather than building a specialized programming language (as we did in Chapter~\ref{ch:impl}), we
discuss the technical requirements for embedding coeffects as a domain-specific language (DSL) into
a statically-typed functional language with rich type system such as Haskell. This can be done by
following the successful example of Haskell's ``do'' notation.

### 2016-05-16 text/Chapter09.tex
Edits in further work and the rest (Chapter 8)
Spell checking

\section{Overview of contributions}
\label{sec:conc-summary}

@@

We use comonads in a syntactic way, following the example of Haskell's use of monads and treat
it as a \emph{translation} from source context-aware programming language to a simple target
functional language. The target language includes uninterpreted comonadically-inspired primitives
whose concrete reduction rules need to be provided for each concrete context-aware deomain-specific
language. We give concrete definitions and prove type safety for three sample context-aware
languages (Section~\ref{sec:semantics-proofs} and Section~\ref{sec:struct-transl}). Together with
well-typedness of our translation, these guarantee that ``well-typed context-aware programs do
not go wrong''.

>>>>

\section{Contributions}
\label{sec:conc-summary}

@@

We use comonads in a syntactic way, following the example of Haskell's use of monads and treat
it as a \emph{translation} from source context-aware programming language to a simple target
functional language. The target language includes uninterpreted comonadically-inspired primitives
whose concrete reduction rules need to be provided for each concrete context-aware domain-specific
language. We give concrete definitions and prove type safety for three sample context-aware
languages (Section~\ref{sec:semantics-proofs} and Section~\ref{sec:struct-transl}). Together with
well-typedness of our translation, these guarantee that ``well-typed context-aware programs do
not go wrong''.
